The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-06 paper/ms.tex
typo

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approah. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

>>>>

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:
